---
title: "Installation Review"
execute: 
  warning: false
  eval: false
---



:::{.callout-note} 

## The package was successfuly installed
... even though it wasn't as easy.

Some packages required to download zips and manually install, some can be installed directly from github. I had the chance to find how to install properly from zipfiles [here](https://github.com/Open-Systems-Pharmacology/OSPSuite-R#under-windows) (It didn't work with `devtools::install_local()` which I usually use). More extensive instructions should be available in the repo's README.

**Questions:**

- Do users in esqlabs have their own installs of RStudio and esqlabsR + dependencies ?
- Do they often encounters bug or environment misconfigurations when upgrading version ?
- What are the most common problem when people want to use the package ?
- Are they users outside of esqlabs ? Who are they ?
:::


## Install the package

Looking for installation from [https://github.com/esqLABS/esqlabsR](https://github.com/esqLABS/esqlabsR). 

::: {.column-margin}
Why is the package not installable from github directly ?
:::


## Install dependencies

According to the Readme file, dependencies must be installed manually.


::: {.column-margin}
What all these dependencies do ?
:::


### rClr
```{r}
download.file("https://github.com/Open-Systems-Pharmacology/rClr/releases/download/v0.9.2/rClr_0.9.2.zip", "_data/rClr.zip")
install.packages("_data/rClr.zip", repos = NULL)
```

### OSPSuite.Rutils & TLF library
```{r}
library(remotes)
remotes::install_github("Open-Systems-Pharmacology/OSPSuite.RUtils")
remotes::install_github("Open-Systems-Pharmacology/TLF-Library")
```

### OSPSuite
```{r}
download.file("https://github.com/Open-Systems-Pharmacology/OSPSuite-R/releases/download/v11.0.123/ospsuite_11.0.123.zip", "_data/ospsuite.zip")
install.packages("_data/ospsuite.zip", repos = NULL)
```

### OSPSuite Parameter Identification
```{r}
remotes::install_github("Open-Systems-Pharmacology/OSPSuite.ParameterIdentification")
```



### Verification

```{r,eval=T,results='hold'}

packageVersion("ospsuite")
packageVersion("tlf")
packageVersion("rClr")
```


## Install esqLABSR 

### Installation process
```{r}
download.file("https://ci.appveyor.com/api/buildjobs/7k0p0h00kkcga9nv/artifacts/esqlabsR.zip", destfile = "_data/esqlabsR.zip")
install.packages("_data/esqlabsR.zip", repos = NULL)
```



### Verification

```{r, eval=TRUE, results='hold'}
library(esqlabsR)
```
 
```{r,eval=T,results='hold'}
find.package("esqlabsR")
packageVersion("esqlabsR")
```


